Component-Based mruby Platform for IoT Devices

### 2018-02-24 ipsj/reply_letter/paper.tex
Update reply letter

\usepackage{a4wide}
\usepackage{graphicx}
\usepackage{fancybox}
\usepackage{ascmac}
\usepackage{xspace}
%\usepackage{pdfpages}
\usepackage{pifont}
\usepackage{array}

@@

@@

Thank you for your suggestion.
The main contribution of this paper is to build a platform for IoT devices with high productivity using mruby.
However, as the reviewer 1 says, the proposed two functionalities, TINET+TECS and TLSF+TECS, can be applicable to various embedded systems because these frameworks are executed on TECS and not limited to mruby.
We added the following sentence in Section 6.

@@

We added the requirements at the beginning of Section 2.
\begin{itembox}[|]{}
{\bf Requrements:} The requirements for proposing the mruby platform for IoT devices are defined as follows.
\begin{description}
    \item[R1:]
        TCP/IP functions can be utilized from mruby programs and the protocol stack can be easily configured for producivity since the network function is essential to the IoT systems.

    \item[R2:]
        Multiple mruby programs can run in pallalel to improve producivity of software development.
        A theread-safe memory allocator is required to prevent the multiple mruby tasks from conflicting their memory.

@@

\begin{enumerate}
\item 
    Table 3 (Modified code lines of CDL) showed the configurability evaluation, but since it is hard to understand, we moved to the beginning of the evaluation section and clarified the point we would like to claim.

\begin{itembox}[|]{Evaluation}
As shown in Table 2, the code lines for modification were measured to demonstrate the improved configurability.
This demonstrated the ability to change the composition of the protocol stack with a small workload, confirming that the proposed framework improves the configurability.
\end{itembox}\\

\item We added evaluations of TLSF+TECS in Section 4.3.
    This section shows a comparison which two diffrent applications are executed with two ways.
    One is to hold its own heap (TLSF+TECS), and the other is to utilize a execulusive control such as semaphore.

@@

\begin{enumerate}
\item
    TODO: 
    We added the execution times with UDP and discussed it.
    Note, we evaluated only TCP and UDP which are supported by TINET.
\begin{itembox}[|]{Evaluation}
Conversely, we evaluated the execution times with UDP as shown in Fig. 29.
TINET+TECS can run at the same speed as TINET; therefore, the overheads of TINET+TECS are low.
\end{itembox}\\

\item
    TODO:
    We added the memory usage of only TCP, only UDP, and both TCP and UDP.

@@

評価部分は，コンポーネント化による実行時間やメモリ消費のオーバヘッドを抑えることができたことを示しています．
コンフィグラビリティ評価を冒頭におき，主張したい点が分かりやすいように変更しました．

@@

ご指摘ありがとうございます．
提案すべきは，「IoTデバイス向けのmrubyプラットフォーム」とし，それを実現するためにTINET+TECSとTLSF+TECSの２つの機能を組み込むという表現に修正を行いました(AbstractおよびIntroduction).
また，問題点と解決策が対応づくように，貢献部分や要件を修正・加筆しました．

@@

% 提案は、「IoTデバイス向けのmrubyプラットフォーム」であり、TINET+TECSとTLSF+TECSの「2つの機能を組み込んだ」とする。
% 貢献部分に、「TINETのコンフィグラビリティを向上させる」「マルチVMを実現する」と追記する。
\end{flushleft}

@@

\begin{itembox}[|]{}
{\bf Requrements:} The requirements for proposing the mruby platform for IoT devices are defined as follows.
\begin{description}
    \item[R1:]
        TCP/IP functions can be utilized from mruby programs and the protocol stack can be easily configured for producivity since the network function is essential to the IoT systems.

    \item[R2:]
        Multiple mruby programs can run in pallalel to improve producivity of software development.
        A theread-safe memory allocator is required to prevent the multiple mruby tasks from conflicting their memory.

@@

上で述べたように，「IoTデバイス向けのmrubyプラットフォーム」を提案し，それを実現するために，２つの機能TINET+TECSとTLSF+TECSを組み込んだというストーリーにしました．
それに伴い，実現するための要件を加筆し，UDPの評価およびTLSF+TECSの評価を付け加えました．
\end{flushleft}

@@

関連研究に，提案フレームワークの利点として，速い実行時間とコンフィグラビリティ性による小さいメモリ消費の2点を加筆しました．

\begin{itembox}[|]{Related work}
mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs.
That is, mruby programs can be executed at the same speed as C, which is faster than other scripting languages.

@@

ご指摘ありがとうございます．
英文校正を依頼し，表現のミスや誤字・脱字の修正を行いました．
\end{flushleft}

@@

ご指摘の通り，引用を追加いたしました．
また，IPSJ論文誌のサンプルを参考にWebの引用について修正を行いました．
\end{flushleft}

>>>>

\usepackage{a4wide}
\usepackage[dvipdfmx]{graphicx}
\usepackage{fancybox}
\usepackage{ascmac}
\usepackage{xspace}
%\usepackage{pdfpages}
\usepackage{pifont}
\usepackage{array}

@@

\section{Response to Meta-reviewer}
\begin{enumerate}

Basically, the proposed framework seems to be useful.
However as the reviewers suggest, this paper is not sophisticated as a research paper including English.

Thank you for the comments.
In order to reflect the comments of reviewers, we fixed abstract and introduction, and added requirements and evaluations such as the execution time and memory consumption of UDP (4.2) and TLSF+TECS (4.4).
Furthermore, we fixed our English in this paper by a native speaker in a proofreading company.
For more detail, please see our replies as follows.

@@

Thank you for your suggestion.
The main contribution of this paper is to build a platform for IoT devices with high productivity using mruby.
We modified Abstract as follows.

However, as the reviewer 1 mentioned, the proposed two functionalities, TINET+TECS and TLSF+TECS, can be applicable to various embedded systems because these frameworks are executed on TECS and not limited to mruby.
We added the following sentence in Section 6.

@@

We added the requirements at the beginning of Section 2.
\begin{itembox}[|]{}
{\bf Requrements:} The requirements of the proposed mruby platform for IoT devices are defined as follows.
\begin{description}
    \item[R1:]
        TCP/IP functions can be utilized from mruby programs and the protocol stack can be easily configured for producivity since the network function is essential to the IoT systems.

    \item[R2:]
        Multiple mruby programs can run concurrently to improve productivity of software development.
        A thread-safe memory allocator is required to prevent the multiple mruby tasks from conflicting their memory.

@@

\begin{enumerate}
\item
    We added the new subsection (4.1) for the configurability evaluation.

\begin{itembox}[|]{4.1 Improved configurability}
As shown in Table 2, the code lines for modification were measured to demonstrate the improved configurability.
This demonstrated the ability to change the composition of the protocol stack with a small workload, confirming that the proposed framework improves the configurability.
\end{itembox}\\

\item
    We added evaluations of TLSF+TECS in Section 4.3.
    This section shows a comparison which two different applications are executed with two ways.
    One is to hold its own heap (TLSF+TECS), and the other is to utilize an exclusive control such as a semaphore.

\begin{itembox}[|]{4.4 Memory usage of RiteVMs by TLSF+TECS}
The proposed dynamic memory allocator, TLSF+TECS, executes multiple tasks without exclusive control concurrently because each TLSF component holds its own heap area.
The TLSF+TECS framework provides functionality to acquire statistical information describing dynamic memory usage.
Therefore, it is possible to analyze the operational status of the TLSF and GC on RiteVMs.
\ldots\ldots

% \begin{figure}[h]
    \centering
    \includegraphics[width=8cm,clip]{../figure/EvaluationOfTLSFStatistics.pdf}
    % \caption{Memory usage of RiteVMs with TLSF+TECS}
    % \label{fig:EvaluationOfTLSFStatistics}
% \end{figure}

\end{itembox}\\

@@

\begin{enumerate}
\item
    We added the execution times with UDP and discussed it.
    Note that we evaluated TCP and UDP which are supported by TINET.

\begin{itembox}[|]{4.2 Performance of TINET+TECS}
Conversely, we evaluated the execution times with UDP as shown in Fig. 29.
TINET+TECS can run at the same speed as TINET; therefore, the overheads of TINET+TECS are low.
\end{itembox}\\

\item
    We added the memory usage of only TCP, only UDP, and both TCP and UDP.

\begin{itembox}[|]{4.2 Performance of TINET+TECS}
\end{itembox}\\

@@

productivityに関する評価(configurability)の節を新規に追加し，主張したい点が分かりやすいように変更しました．
execution timeとmemory consumptionの評価は，提案フレームワークを用いたオーバヘッドが小さいことを示しています．

\begin{itembox}[|]{4.1 Improved configurability}
As shown in Table 2, the code lines for modification were measured to demonstrate the improved configurability.
This demonstrated the ability to change the composition of the protocol stack with a small workload, confirming that the proposed framework improves the configurability.
\end{itembox}\\

@@

ご指摘ありがとうございます．
提案すべきは，「IoTデバイス向けのmrubyプラットフォーム」とし，それを実現するためにTINET+TECSとTLSF+TECSの２つの機能を組み込むという表現に修正を行いました(AbstractおよびIntroduction).
さらに，問題点と解決策が対応づくように，Introductionの貢献部分や要件(2章)を修正・加筆いたしました．

@@

@@

\begin{itembox}[|]{}
{\bf Requrements:} The requirements of the proposed mruby platform for IoT devices are defined as follows.
\begin{description}
    \item[R1:]
        TCP/IP functions can be utilized from mruby programs and the protocol stack can be easily configured for producivity since the network function is essential to the IoT systems.

    \item[R2:]
        Multiple mruby programs can run in pallalel to improve producivity of software development.
        A thread-safe memory allocator is required to prevent the multiple mruby tasks from conflicting their memory.

@@

上で述べた通り，「IoTデバイス向けのmrubyプラットフォーム」を提案し，それを実現するために，２つの機能TINET+TECSとTLSF+TECSを組み込んだというストーリーにしました．
それに伴い，実現するための要件を加筆し，UDPの評価およびTLSF+TECSの評価を付け加えました．
\end{flushleft}

@@

提案フレームワークの利点として，速い実行時間とコンフィグラビリティ性による小さいメモリ消費の2点を関連研究に加筆いたしました．

\begin{itembox}[|]{Related work}
mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs [9].
That is, mruby programs can be executed at the same speed as C, which is faster than other scripting languages.

@@

ご指摘ありがとうございます．
英文校正業者にネイティブ校正を依頼し，ご指摘頂いた点を含め，表現のミスや誤字・脱字の修正を行いました．
\end{flushleft}

@@

ご指摘の通り，引用を追加いたしました．
IPSJ論文誌のサンプルを参考にWebの引用について修正を行いました．
\end{flushleft}
